analysis

### 2020-05-29 analysis.Rmd
added 2010 and 2011 GAM analysis

>>>>

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
plot(sm(bb_rich_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")
```
#### 2011
```{r}
### Per-capita resource availability
percap_yday <- gam(log(fl.per.bb) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2011),
                   method = "REML")

percap_gdd <- gam(log(fl.per.bb) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div, year == 2011),
                  method = "REML")

webass_yday <- gam(log(web.asymmetry) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div_trans, year == 2011),
                   method = "REML")

webass_gdd <- gam(log(web.asymmetry) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div_trans, year == 2011),
                  method = "REML")

### Floral abundance
fl_abund_yday <- gam(log(fl.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

fl_abund_gdd <- gam(log(fl.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

### BB abundance
bb_abund_yday <- gam(log(bb.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_abund_gdd <- gam(log(bb.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

### BB richness
bb_rich_yday <- gam(log(bb.rich) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_rich_gdd <- gam(log(bb.rich) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
plot(sm(bb_rich_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")
```
#### 2010
```{r}
### Per-capita resource availability
percap_yday <- gam(log(fl.per.bb) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2010),
                   method = "REML")

percap_gdd <- gam(log(fl.per.bb) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div, year == 2010),
                  method = "REML")

webass_yday <- gam(log(web.asymmetry) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div_trans, year == 2010),
                   method = "REML")

webass_gdd <- gam(log(web.asymmetry) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div_trans, year == 2010),
                  method = "REML")

### Floral abundance
fl_abund_yday <- gam(log(fl.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

fl_abund_gdd <- gam(log(fl.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

### BB abundance
bb_abund_yday <- gam(log(bb.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_abund_gdd <- gam(log(bb.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

### BB richness
bb_rich_yday <- gam(log(bb.rich) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_rich_gdd <- gam(log(bb.rich) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")
